### 2016-11-23 Manuscript/SW_early_life_telomeres.Rmd
EDS

#####Telomere dynamics and age
Using cross-sectional data we found that RTL decreased with age in the Seychelles warbler (LMM: estimate = `r round3(fixef(RTL_Age)['Agemonths'],lessthan = F)`, CIs = `r paste(round3(CIwald(RTL_Age)['Agemonths',],lessthan = F),collapse = ', ')`). RTL also decreased with log-transformed age (LMM: estimate = `r round2(fixef(RTL_LogAge)['LogAge'])`, CIs = `r paste(round2(CIwald(RTL_LogAge)['LogAge',]),collapse = ', ')`), and this model was a significantly better fit than one modelling a linear relationship between RTL and age (P = `r round3(anova(RTL_Age,RTL_LogAge)$"Pr(>Chisq)"[2])`), suggesting that telomere length decreased at the greatest rate in early life - something that was evident from the raw data (Fig. 1A). Also worth noting is that while the overall trend was for decreasing RTL, there were appoarent increases in cross-sectional telomere length after one year of age and at several points later in life (Fig. 1A). Using longitudinal data, we found that RTL decreased with $\Delta$Age (LMM: estimate = `r round3(fixef(RTL_DeltaAge)['DeltaAge'],lessthan = F)`, CIs = `r paste(round3(CIwald(RTL_DeltaAge)['DeltaAge',],lessthan = F),collapse = ', ')`), showing that telomere length decreases with age within individuals (Fig. 1B).

Including birth year as a random effect in a LMM of RTL and (log) age resulted in a significantly improved model to one with only individual ID and plate ID as random effects (likelihood ratio test, P `r round3(anova(RTL_LogAge,RTL_LogAge_LY)$"Pr(>Chisq)"[2])`). Furthermore, allowing the slope of the age effect to vary among birth years resulted in a significant improvement on one in which only the intercept was allowed to vary (conditional R^2^ = `r round2(r.squaredGLMM(RTL_LogAge_AgeLY)['R2c'])`; P = `r round3(anova(RTL_LogAge_LY,RTL_LogAge_AgeLY)$"Pr(>Chisq)"[2])`; Fig. 2B). Temporal dynamics of longitudinal telomere data were similar to the cross-sectional data.  A model of RTL and $\Delta$Age including catch year as a random effect was not better than one that did not allow for temporal variation in RTL (P = `r round3(anova(RTL_DeltaAge,RTL_DeltaAge_LY)$"Pr(>Chisq)"[2])`). However a model allowing the slope of the $\Delta$Age effect was not better than one in which only the intercept varied (P = `r round3(anova(RTL_DeltaAge,RTL_DeltaAge_AgeLY)$"Pr(>Chisq)"[2])`).

>>>>

#####Telomere dynamics and age
Model comparison

### 2016-11-23 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
EDS

AIC(RTL_LogAge)
AIC(RTL_LogAge_LY)

@@

dd$FAge <- factor(dd$Agemonths)
dd$Cohort <- factor(dd$LayYear)

lm1 <- lmer(RTL ~ Cohort*(Agemonths + LogAge + FAge) + (1|BirdID) + (1|CatchYear) + (1|PlateID),data=dd,REML = FALSE)

lm2 <- dredge(lm1,subset = !(LogAge & FAge) & !(LogAge & Agemonths ) & !(Agemonths & FAge))

lm2

>>>>

t1 <- as.matrix(RTL_Age_Dredge)

#Sort out row/col names
nams <- colnames(t1)

nams[nams == 'Agemonths'] <- 'Age (continuous)'
nams[nams == 'LogAge'] <- 'Log age'
nams[nams == 'FAge'] <- 'Age (factor)'
nams[nams == 'Cohort:FAge'] <- 'Age (factor)*cohort'
nams[nams == 'Cohort:Agemonths'] <- 'Age (continuous)*cohort'
nams[nams == 'Cohort:LogAge'] <- 'Log age*cohort'

colnames(t1) <- nams

tableS1 <- data.frame(Model = apply(t1,1,getterms,c(2:8)),t1[,c('df','AICc','delta','weight')],stringsAsFactors = FALSE)
colnames(tableS1) <- c('Model','df','AICc', 'Delta AICc','Weight')
rownames(tableS1) <- NULL
tableS1$Model[tableS1$Model == ''] <- 'Null model'
tableS1[,3:5] <- lapply(tableS1[,3:5],as.numeric)
kable(tableS1,digits=3)

@@
